---
title: "Exercise12"
format: html
---

## Load Packages & Data

```{r}
library(tidyverse)
library(naniar)
d <- read_tsv("https://raw.githubusercontent.com/difiore/ada-2024-datasets/main/Mammal_lifehistories_v2.txt")
```
## Step 1: replace -999 with NA

Use *replace_with_na_all* function from {naniar}
```{r}
d <- d %>% replace_with_na_all(condition=~.x==-999)
d
```

## Step 2: drop litter size and refs
```{r}
d <- d %>% select(!c("litter size", refs))
d
```

## Step 3: Log transform all numeric variables

```{r}
d <- d %>% mutate(across(where(is.numeric), log))
d
```

## Step 4: Regress variables

```{r}
m1 <- lm(data=d, `mass(g)`~ `gestation(mo)`,na.action=na.exclude)
r1 <- resid(m1)
m2 <- lm(data=d, `mass(g)`~ `weaning(mo)`,na.action=na.exclude)
r2 <- resid(m2)
m3 <- lm(data=d, `mass(g)`~ `AFR(mo)`,na.action=na.exclude)
r3 <- resid(m3)
m4 <- lm(data=d, `mass(g)`~ `max. life(mo)`,na.action=na.exclude)
r4 <- resid(m4)
m5 <- lm(data=d, `mass(g)`~ `newborn(g)`,na.action=na.exclude)
r5 <- resid(m5)
m6 <- lm(data=d, `mass(g)`~ `wean mass(g)`,na.action=na.exclude)
r6 <- resid(m6)
```

```{r}
d <- d %>% mutate(relGest=r1, relWean=r2, relAFR=r3, relLife=r4, relNewbornMass=r5, relWeaningMass=r6)
d
```

## Step 5: plots
#### RelLife by Order:
```{r}
p1 <- ggplot(d, aes(x=order, y=relLife)) + geom_boxplot() + theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1))
p1
```
Perissodactyla seems to have the highest mean residual lifespan, though Cetacea has the highest when considering the 95% confidence interval.

#### RelNewbornMass by Order
```{r}
p2 <- ggplot(d, aes(x=order, y=relNewbornMass)) + geom_boxplot() + theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1))
p2
```
Carnivora has the highest residual newborn mass.

#### RelWeaningMass by Order
```{r}
p3 <- ggplot(d, aes(x=order, y=relWeaningMass)) + geom_boxplot() + theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1))
p3
```

Pholidota has the highest mean resdual weaning mass, although Lagomorpha seems to have the highest when considering the 95% confidence interval.

## Step 6

```{r}
d<-d%>%drop_na(`max. life(mo)`,`AFR(mo)`, `gestation(mo)` , `newborn(g)`, `weaning(mo)`, `wean mass(g)`, `litters/year`,`mass(g)`)
library(MASS)
```

```{r}
m7 <- lm(data=d, `max. life(mo)` ~ `gestation(mo)` + `newborn(g)` + `weaning(mo)` + `wean mass(g)` + `litters/year` + `mass(g)`)

s1 <- stepAIC(m7, scope=.~., direction="both")
```

```{r}
summary(s1)
```

```{r}
m8 <- lm(data=d, `AFR(mo)` ~ `gestation(mo)` + `newborn(g)` + `weaning(mo)` + `wean mass(g)` + `litters/year` + `mass(g)`)

s2 <- stepAIC(m8, scope=.~., direction="both")
```

```{r}
summary(s2)
```

Wean mass(g) and newborn(g) tend to appear in the 'top models'